Herring: case study 1

### 2016-10-02 diversity/analysis/herring_case_study.Rmd
updated case study

herring = cfec[substr(cfec$p_fshy,1,1) %in% c("L","G"),]

herring_summary = group_by(herring, p_fshy, year) %>%
  summarize(g = sum(g_earn), p = mean(g_price,na.rm=T), lbs = sum(g_pounds), people = length(unique(p_holder))) %>%
  group_by(p_fshy) %>%
  mutate(n = length(unique(year)), maxpeople = max(people,na.rm=T)) %>%
  filter(n > 9) %>%
  filter(maxpeople > 25)
```

>>>>

herring = cfec[substr(cfec$p_fshy,1,1) %in% c("L","G","H"),]

herring_summary = group_by(herring, p_fshy, year) %>%
  summarize(g = sum(g_earn), p = mean(g_price,na.rm=T), lbs = sum(g_pounds), people = length(unique(p_holder))) %>%
  group_by(p_fshy) %>%
  mutate(n = length(unique(year)), maxpeople = max(people,na.rm=T)) %>%
  filter(n > 9) %>%
  filter(maxpeople > 25)

quitters = group_by(herring, p_holder, p_fshy) %>%
  summarize(lastYear = max(year))

group_by(quitters[quitters$lastYear<2014,],lastYear,p_fshy) %>% 
  summarize(n = n()) %>% 
  ggplot(aes(lastYear,n)) + geom_line() + facet_wrap(~p_fshy, scale="free_y") + xlab("Year") + ylab("People leaving the fishery (last year fished)")

# look at what these people did after leaving
cfec_quitters = cfec[which(cfec$p_holder%in%unique(quitters$p_holder)),]
cfec_quitters = left_join(cfec_quitters, quitters[,c("p_holder","lastYear")])

fates = as.data.frame(group_by(cfec_quitters, p_holder, p_fshy) %>% 
  summarize(n = length(which(year > lastYear[1]))) %>% 
  group_by(p_fshy) %>% 
  summarize(n0 = length(which(n==0)), nOther = length(which(n>0))))

trackQuitters = function(permit) {
cfec2= cfec_quitters[which(cfec_quitters$p_holder %in% unique(quitters[quitters$p_fshy==permit,]$p_holder)),]
cfec2 = cfec2[which(cfec2$year > cfec2$lastYear),]
cfec2$SPEC = substr(cfec2$p_fshy,1,1)
totalpermit = group_by(cfec2,SPEC) %>% 
  summarize(g = sum(g_earn))
totalpermit$g = totalpermit$g/sum(totalpermit$g)
return(as.data.frame(arrange(totalpermit,-g)))

}

#trackQuitters("L 21C")
```
